Missing the Point$\colon$ Non-Convergence in Iterative Imputation Procedures

### 2020-04-24 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Edit figures in Results section manuscript.

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 4.8, fig.height = 3.6, echo = FALSE, fig.align = "center") 
```

@@

```{r diagram, out.width="\\linewidth", include=TRUE, fig.align="center", fig.cap="Scheme of the main steps in multiple imputation."}
knitr::include_graphics("./images/diagram.pdf") #adapted from [@buur18] par. 1.4.1.
```

@@

@@

```{r load-res, include = FALSE}
# load("../Results/test.Rdata")
# source("../2.CreateFigures.R")
```

```{r res-univ}
# mean_bias + plot_annotation(title = "Bias in mean estimate, convergence of chain means")
# mean_Rh 
# mean_ACF + plot_annotation(title = "Dotted lines are old $AC$ computation, solid are new.")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 4.8, echo = FALSE, fig.align = "center") 
# knitr::opts_chunk$set(fig.width = 4.8, fig.height = 3.6, echo = FALSE, fig.align = "center")

# packages
library(ggplot2)
library(patchwork)

# results and functions
load("../Results/complete.Rdata")
source("../2.CreateFigures.R")

# default graphing behavior
theme_update(
  plot.title = element_text(hjust = 0.5),
  plot.subtitle = element_text(hjust = 0.5),
  panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  axis.line = element_line(colour = "black"),
  legend.key = element_blank(),
  legend.position = "bottom",
  legend.margin = margin(0,0,0,0),
  # adjust text size
  text = element_text(size = 8),
  title = element_text(size = 8)
  # axis.title = element_text(size = 8),
  # axis.text = element_text(size = 7),
  # legend.text = element_text(size = 7)
)
```

@@

```{r diagram, out.width="\\linewidth", include=TRUE, fig.cap="Scheme of the main steps in multiple imputation."}
knitr::include_graphics("./images/diagram.pdf") #adapted from [@buur18] par. 1.4.1.
```

@@

```{r diagnostics, fig.cap="Convergence diagnostics pathological non-convergence versus typical convergence."}
load("./images/diagnostics_plot.Rdata")
diagnostics_plot
```

@@

```{r mean, fig.height = 6.8, fig.cap="Convergence diagnostics chain mean."}
mean_Rh + mean_AC + mean_bias + plot_layout(guides = "collect", ncol = 1) + plot_annotation(title = "Performance of convergence diagnostics", subtitle = bquote(theta ~ "= chain mean of Y in" ~ y[imp][",m"] ~ "; Q = " ~ mu[Y] ~ "= 25.81"))
```

```{r sd, fig.height = 6.8, fig.cap="Convergence diagnostics chain variance."}
var_Rh + var_AC + sd_bias + plot_layout(guides = "collect", ncol = 1) + plot_annotation(title = "Performance of convergence diagnostics", subtitle = bquote(theta ~ "= chain variance of Y in" ~ y[imp][",m"] ~ "; Q = " ~ sigma[Y] ~ "= 11.32"))
```
```{r est, fig.height = 6.8, fig.cap="Convergence diagnostics regression coefficient."}
est_Rh + est_AC + est_bias + plot_layout(guides = "collect", ncol = 1) + plot_annotation(title = "Performance of convergence diagnostics", subtitle = bquote(theta ~ "= " ~ hat(beta)[2] ~ "in {" ~ y[obs] ~ "," ~ y[imp][",m"] ~ "}" ~ "; Q = " ~ beta[2] ~ "= 2.06"))
```

```{r pred, fig.height = 6.8, fig.cap="Convergence diagnostics regression coefficient."}
PCA_Rh + PCA_AC + Rsq_bias + plot_layout(guides = "collect", ncol = 1) + plot_annotation(title = "Performance of convergence diagnostics", subtitle = bquote(theta ~ "= first eigenvalue of" ~ Sigma ~ "in {" ~ y[obs] ~ "," ~ y[imp][",m"] ~ "}" ~ "; Q = explained variance = 19.25"))
